%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\usepackage{etaremune}
\usepackage{enumitem}

\name{Flavio Toffalini} % Your name
%\address{XXX \\ Lausanne, Switzerland, } % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary =addess (optional)
\address{(+39)~$\cdot$~340 255 9962 \\ flavio.toffalini@rub.de} % 
%Your phone number and email

\begin{document}
	
My research interest covers many aspects of system security. My Ph.D. background
focuses on software security for Trusted Execution Environment. 

\begin{rSection}{Current Position: Assistant Professor}
	
	{\bf Ruhr-Universität Bochum (RUB), Germany} 
	\hfill {\em Sep 2024 to Now} \\
	Assistant Professor in Automated Security Analysis

\end{rSection}

\begin{rSection}{Former Position}
	
	{\bf \'Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Switzerland} 
	\hfill {\em Nov 2021 -- Aug 2024} \\
	PostDoc, supervised by Prof. Mathias Payer \\
	Topic: fuzzing, mitigation, software analysis

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
    
{\bf Singapore University of Technology and Design, Singapore} \hfill {\em Jan
2017 - Sep 2021} \\
Ph.D., supervisor Prof. Jianying Zhou \\
Topic: trusted computing, system security \\
Thesis Title: Challenges, threats, and novel defenses for Trusted Execution
Environments

{\bf University of Verona, Italy} \hfill {\em Sep 2012 - Oct 2015} \\
M.S. in Computer Science and Engineering 108$/$110, GPA 3,9/4 \\
Supervisor Prof. Damiano Carra \\
Master thesis topic: Google dorks, Web security


{\bf University of Pavia, Italy} \hfill {\em Sep 2006 - Dec 2009} \\ 
B.S. in Computer Engineer 101$/$110, GPA 3,67/4 \\
Supervisor Prof. Paolo Gamba \\


\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Academic Activities}

\begin{rSubsection}{King's College London}{Nov 2019 - Mar 2020}{Visiting 
fellow, supervised by Prof. Lorenzo Cavallaro}{London, UK}
	\item Topic: trusted computing, system security
\end{rSubsection}

\begin{rSubsection}{University of Padua}{Jan 2018 - Aug 2018}{Visiting fellow, supervised by Prof. Mauro Conti}{Padua, Italy}
    \item Topic: trusted computing, system security
\end{rSubsection}

% \begin{rSubsection}{Singapore University of Technology and Design}{Aug 2016 - Dec 2017}{Research Assistant, supervised by Prof. Mart\'in Ochoa}{Singapore, Singapore}
%     \item Topic: insider threats, trusted computing
% \end{rSubsection}

\begin{rSubsection}{University of Verona}{Dec 2015 - July 2016}{Research Assistant, supervised by Prof. Fausto Spoto}{Verona, Italy}
\item Topic: static analysis of Android applications
\end{rSubsection}

\begin{rSubsection}{Eurecom}{April 2015 - July 2015}{Visiting fellow, supervised by Prof. Davide Balzarotti}{Biot, France}
\item Topic: Google dorks, Web security
\end{rSubsection}

\newpage
\begin{rSection}{Teaching Activites}
\item ``Advanced Automatic Testing'' (Master Course, Main Instructor) at Ruhr-Universität Bochum, 48 hours
\item ``Seminar in Advanced Automatic Testing'' (Master/Bachelor Seminar, Main Instructor) at Ruhr-Universität Bochum, 48 hours
\end{rSection}

\begin{rSection}{Supervision}
\item PhDs: Currently 1, 2 co-supervised during Post-Doctoral
\item MSc: Currently 3, 3 successfully completed
\item BSc: 3 successfully completed
\item Interns: Currently 1, 1 successfully completed
\end{rSection}

\begin{rSection}{Research Grants}
\item ``Advancing Cybersecurity Through Semantic Bugs in Interpreted Programming
Languages'' (PI) funded by the Deutsche Forschungsgemeinschaft (DFG, German
Research Foundation) under Germany's Excellence Strategy - EXC 2092 CASA -
390781972 (approved from 2025 to 2028)
% \item ``Hermes--Large Scale Harness Generation for Robust Library Testing'' (PI)
% Individual Research Grants (DFG, German Research Foundation) - TO 1883/1 -
% (under review, expected from 2026 to 2029)
\item ``Detecting Semantic Bugs in JavaScript Engines'' unrestricted git from Google
Research Scholar (\$60,000 USD)
\end{rSection}

\end{rSection}

\begin{rSection}{Publications}

% \begin{rSeparator}{2023}
% \end{rSeparator}

% \begin{rSubsection}{Crystallizer: A Hybrid Path Analysis Framework To Aid in
% 	Uncovering Deserialization Vulnerabilities}{major reviion -
% 	2023}{Major revision at Foundations of Software Engineering (FSE)}{}
% 	\item Srivastava P., \textbf{Toffalini F.}, Vorobyov K., Gauthier F.,
% 	Bianchi A, and Payer M.
% \end{rSubsection}


\input{publication}
    
\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Academic Service}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
NDSS reviewer 2022/23/24/25/26 \\
Usenix SEC 2025/26 \\
DIMVA reviewer 2022/23/24/25 \\
DIMVA poster chair 2024/25 \\
ACSAC reviewer 2024/25 \\
ISSTA reviewer 2024/25 \\
TOSEM reviewer 2024 \\
Usenix SEC AE reviewer 2022 \\
EuroSP shadow-reviewer 2020 \\
TIFS reviewer 2018/19 \\
\end{tabular}

\end{rSection}

\begin{rSection}{Other Activites}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Employee in IT Companies: 2009-2011\\
Part-time Student during Master: 2012-2014\\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
